Fig3

### 2020-02-10 analysis/figure-1.Rmd
better fig 1 and 3

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(factoextra)
library(cowplot)
library(Rtsne)
library(viridis)
library(forcats)

@@

```{r tSNE-df}
# prep for tsne

@@

```{r }

plottsneelipse <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 2, aes(color = tissue )) 
  return(p)
}

@@

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 12, rel_heights = c(0.5,1))
abcde
```

## pca

```{r supplfig1}
charpca <- subsetmakepca(tissuelevels, charlevels, sexlevels)	
charfviz <- makefvizdf(tissuelevels, charlevels, sexlevels)

f <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = c(0.6,0.2), 
        #legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = "tissue * treatment")   
g <- plotfriz(charfviz) + labs(subtitle = "  ")

pcaplots <- plot_grid(f,g, labels = c("f", "g"), label_size = 12, align = "hv")
pcaplots
```

## PRL

```{r}
PRLplot <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "treatment * sex, pituitary only") + 
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))

fgh <- plot_grid(pcaplots, PRLplot, labels = c(" ", "h"), label_size = 12)
fgh
```

## all together now

```{r fig1, fig.width=7, fig.height=6}
plot_grid(abcde, fgh, nrow = 2, rel_heights = c(2,1.5))
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)

@@

```{r tSNE-df}

# prep for tsne

@@

```{r fig1, fig.width=7, fig.height=6}

plottsneelipse <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 1, aes(color = tissue )) 
  return(p)
}

@@

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 12, rel_heights = c(0.5,1))

plottsneelipsev2 <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 1, aes(color = treatment)) 
  return(p)
}

h <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + labs(subtitle = "hypothalamus")  + facet_wrap(~sex)
i <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + labs(subtitle = "pituitary", y = NULL) + facet_wrap(~sex) 
j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + labs(subtitle = "gonads", y = NULL)  + facet_wrap(~sex)

hij <- plot_grid(h,i,j, nrow = 1, labels = c("h", "i", "j"), label_size = 12)

fig1 <- plot_grid(abcde, hij, nrow = 2, rel_heights = c(0.6,0.4))
fig1
```

### 2020-02-10 analysis/figure-3.Rmd
better fig 1 and 3

# Plots with Prolactin

```{r}
library(tidyverse)
library(cowplot)
library(magick)
library(png)
library(grid)
library(ggimage)
library(apaTables)

source("../R/themes.R") 
source("../R/functions.R")
source("../R/icons.R")

@@

## Circulating levels of prolactin and prolactin expression

```{r data}
prolactin <- read_csv("../results/07_hormones.csv") %>%
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() 
prolactin$treatment <- factor(prolactin$treatment, levels = alllevels)

@@

```{r fig3, fig.width=7}

a <- plotprolactin(PRLhyp, PRLhyp$counts, "PRL", "hypothalamus") + 
  theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))
b <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "pituitary") + 
  theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))
c <- plotprolactin(prolactin, prolactin$plasma_conc, "prolactin (ng/mL)", "blood") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) 
d <- plotprolactin(PRLgon, PRLgon$counts, "PRL", "gonads") + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(face = "italic"))

mylegend <- plotprolactin(PRLvsd, PRLvsd$counts, "PRL", "gonads") +
  theme(legend.position = "bottom",
        legend.direction = "vertical",
        legend.key.size = unit(0.5, 'lines')) +
  guides(color = guide_legend(ncol = 1),
         shape = guide_legend(ncol = 1))
mylegend <- get_legend(mylegend)

allPLRplots <- plot_grid(a,b,c,d, labels = "auto", rel_heights = c(0.425,0.575))

fig3 <- plot_grid(allPLRplots, mylegend , nrow = 2, rel_heights = c(1,0.2))
fig3
```

>>>>

# Figure 3

```{r setup}
library(tidyverse)
library(cowplot)
library(ggimage)
library(apaTables)
library(factoextra)

source("../R/themes.R") 
source("../R/functions.R")
source("../R/icons.R")
source("../R/wrangledata.R")

@@

## Data: PCA, hormones, PRL expression

```{r data}
# pca
charpca <- subsetmakepca(tissuelevels, charlevels, sexlevels)	
charfviz <- makefvizdf(tissuelevels, charlevels, sexlevels)

# hormones
prolactin <- read_csv("../results/07_hormones.csv") %>%
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() 
prolactin$treatment <- factor(prolactin$treatment, levels = alllevels)

# PRL vsd

vsd_path <- "../results/DEseq2/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

PRLvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") %>%
  filter(gene == "PRL")  %>%
  dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
  dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
  dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
  dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
  dplyr::select(sex, tissue, treatment, gene, samples, counts)
PRLvsd$treatment <- factor(PRLvsd$treatment, levels = alllevels)

PRLhyp <- PRLvsd %>% filter(tissue == "hypothalamus")
PRLpit <- PRLvsd %>% filter(tissue == "pituitary")
PRLgon <- PRLvsd %>% filter(tissue == "gonad")
```

```{r fig3, fig.width=7, fig.height=7}

a <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = c(0.6,0.1), 
        legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = " ")

b <- plotprolactin(PRLhyp, PRLhyp$counts, "PRL", "hypothalamus") + 
  theme(legend.position = c(0.7,0.9), axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"),
        legend.title = element_blank()) + guides(fill = F)

c <- plotfriz(charfviz) + labs(subtitle = "  ")

d <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "pituitary") + 
  theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))

e <- plotprolactin(prolactin, prolactin$plasma_conc, "prolactin (ng/mL)", "blood") +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

f <- plotprolactin(PRLgon, PRLgon$counts, "PRL", "gonads") + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(face = "italic"))

plot_grid(a,b,c,d,e,f, labels = "auto", ncol = 2, rel_heights = c(1,1,1.2))

@@
